Inpainting with dimensionality reduction in the Fourier domain

### 2011-06-17 project/Paper/paper.tex

\begin{figure}[tbp]
  \centering
  \includegraphics[width=\columnwidth]{images/imageFraming}
  \caption{Only the inner patch (marked red) is reconstructed in one step while the frame only provides additional signal. (Undistorted image shown) }
  \label{fig:framing}
\end{figure}
\begin{figure}[htbp]
  \centering
  \includegraphics[width=\columnwidth]{images/local_wdenoised_1d}
  \caption{Signal compression and denoising using the Daubechies wavelet basis.}
  \label{fig:denoise-wavelet}
\end{figure}

Use examples and illustrations to clarify ideas and results. For
example, by comparing Figure~\ref{fig:framing} and
Figure~\ref{fig:denoise-wavelet}, we can see the two different
situations where Fourier and wavelet basis perform well.

>>>>

\begin{figure}[tbp]
  \centering
  \includegraphics[width=\columnwidth]{images/boundaryArtifact_noframe}
  \caption{Artifacts that occur without a frame (frame size = 0). The patches are recognizable in the reconstruction}
  \label{fig:boundaryArtifacts}
\end{figure}

\begin{figure}[tbp]
  \centering
  \includegraphics[width=\columnwidth]{images/imageFraming}
  \caption{Only the inner patch (marked red) is reconstructed in one step while the frame only provides additional signal. (Undistorted image shown) }
  \label{fig:framing}
\end{figure}

((( TODO: Plot missingPixel\% vs. accuracy (vs. speed?) )))

Use examples and illustrations to clarify ideas and results. For
example, by comparing Figure~\ref{fig:framing} and
Figure~\ref{fig:flowchart}, we can see the two different
situations where Fourier and wavelet basis perform well.
